---
title: "Decoding Airbnb: Price Influences in New York City"
author: "Jessica Wang"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

This project conducts an exploratory analysis of the Airbnb Open Data from Kaggle to investigate the factors that significantly influence Airbnb listing prices in New York City. By analyzing data spanning from 2008 to 2022, the project aims to uncover patterns and correlations between listing attributes such as location, ratings, and price. 

```{r echo=FALSE, message=FALSE}
source("Project.R")
```


## Showcasing plots {.tabset}

### Figure 1

```{r echo=FALSE}
# Listing Price by Boroughs
p1 = ggplot(df, aes(x = `neighbourhood group`, y = price)) +
  geom_boxplot() +
  labs(title = "Airbnb Listing Price by Borough",
       x = "Boroughs in New York City",
       y = "Price") +
  theme(legend.position = "bottom")
ggplotly(p1)
```

### Figure 2

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Facet plot by neighbourhoods (with top 5 number of listings) showing scatterplots with linear regression lines of the total number of reviews and prices

top_5 <- df %>% group_by(neighbourhood) %>%
  summarise(Count=n())  %>%
  arrange(desc(Count)) %>%
  top_n(5, wt=Count)

df_selected_neighbourhoods <- df %>% 
  filter(neighbourhood %in% top_5$neighbourhood)

# Create the facet plot
p2 = ggplot(df_selected_neighbourhoods, aes(x = `number of reviews`, y = price)) +
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~neighbourhood) + 
  labs(title = "Airbnb Listing Price vs Total Number of Reviews",
       x = "Total Number of Reviews",
       y = "Airbnb Listing Price") 

ggplotly(p2)
```


