---
title: "Decoding Airbnb: Price Influences in New York City"
author: "Jessica Wang"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
        css: styles.css
        theme: cosmo
---

# Overview

This project conducts an exploratory analysis of Airbnb listing data from New York City, sourced from the open dataset available on Kaggle. The focus is on understanding the various factors that influence the pricing of Airbnb listings, with an aim to provide insights that could benefit hosts, guests, and policymakers engaged with the sharing economy.

## Project Introduction

Airbnb has transformed the way people travel and experience new locations by providing unique lodging options that range from simple rooms to entire homes. Understanding what drives the pricing of these listings is crucial for stakeholders to make informed decisions. This analysis explores data spanning from 2008 to 2022, examining attributes such as geographical location, customer ratings, and other relevant factors.

## Research Question

The primary question guiding this study is: "What factors significantly influence the price of an Airbnb house listing in New York City?" We hypothesize that variables such as location, ratings, and the type of accommodation play significant roles in shaping pricing strategies.

## Significance of the Study

The findings from this study are intended to:

- Help Airbnb hosts set competitive and fair prices for their accommodations.
- Assist guests in finding the best possible lodging options within their budget.
- Offer policymakers data-driven insights into the impact of short-term rentals on local housing markets and tourism.

## Data

The processed dataset comprises 68,428 observations. Key variables relevant to this study are summarized in the sections below. Discrete variables are analyzed for their frequency distribution, with percentages. Continuous variables are summarized using their median values and interquartile ranges in the format: Median (Lower Quartile, Upper Quartile).

```{r echo=FALSE, message=FALSE}
source("Processed_Data.R")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
library(gtsummary)
library(gt)

table1 <- 
  df %>%
  tbl_summary(include = c(host_identity_verified, `minimum nights`, `neighbourhood group`, instant_bookable), label = c(host_identity_verified ~ "Host Verified", `minimum nights` ~ "Minimum Nights Requirement",  `neighbourhood group` ~ "Boroughs", instant_bookable~"Instant Bookable")) %>%
  as_gt() %>%
  gt::as_raw_html()


table2 <- 
  df %>%
  tbl_summary(include = c(`review rate number`, `room type`, cancellation_policy, `Construction year`, price, `service fee`,`number of reviews`, `availability 365`, `reviews per month`), label= c(`Construction year`~ "Construction Year", price~"Listing Price", `service fee`~ "Service Fee", `number of reviews`~"Total Number of Reviews", `availability 365`~"Number of Days This Listing is Available", `reviews per month`~"Reviews per Month", `review rate number`~"Ratings", `room type`~"Room Type", cancellation_policy~"Cancellation Policy")) %>% 
  as_gt() %>%
  gt::as_raw_html()

cat('<div style="display: flex; justify-content: space-between;">')
cat('<div style="width: 50%;">', table1, '</div>')
cat('<div style="width: 50%;">', table2, '</div>')
cat('</div>')
```

