---
title: "Decoding Airbnb: Price Influences in New York City"
author: "Jessica Wang"
output: 
    html_document:
        toc: TRUE
        toc_float: TRUE
---

```{r echo=FALSE, message=FALSE}
source("Processed_Data.R")
```


## Showcasing plots {.tabset}

### Figure 1

```{r echo=FALSE}

stopwords2 <- c(stopwords("english"), "nyc", "room", "bedroom", "bed", "manhattan", "williamsburg", "brooklyn", "w", "apartment", "studio", "apt", "loft", "bushwick", "location", "one")

topwords <- df |>
  unnest_tokens(word, NAME, token="words") |>
  filter(!word %in% stopwords2) |>
  filter(!str_detect(word, "\\d")) |> # also filter out numbers
  count(word, sort=T) |>
  head(20)
  
filtered_data <- df |>
  unnest_tokens(word, NAME, token="words") |>
  filter(word %in% topwords$word)

# Plotting the price boxplot for each keyword
p1 <- ggplot(filtered_data, aes(x = word, y = price)) +
  geom_boxplot() +
  coord_flip() + 
  labs(title = "Airbnb Listing Prices by Top Keywords",
       x = "Keyword",
       y = "Price") +
  theme_minimal()

ggplotly(p1)
```

This boxplot illustrates the variation in median prices associated with the top 20 most frequently used keywords in Airbnb listing titles across New York City. Notably, despite its frequent usage, the keyword 'luxury' is associated with lower median prices, while 'village' and 'quiet' tend to command higher prices, highlighting the influence of specific descriptive terms on pricing perceptions. This visualization underscores the impact of keyword selection on potential pricing strategies within the Airbnb market.

### Figure 2

```{r, message=FALSE, echo=FALSE}
# Listing Price by Neighborhoods 
neighbourhoods_price_df <- df %>%
  group_by(neighbourhood) %>%
  summarise(MeanPrice=mean(price), MeanLat=mean(lat), MeanLong=mean(long), )  %>%
  arrange(desc(MeanPrice))

top_places <- neighbourhoods_price_df %>% top_n(10, wt=MeanPrice)

# Plot the map
pal <- colorNumeric(
  palette = "viridis",
  domain = neighbourhoods_price_df$MeanPrice
  )

leaflet(neighbourhoods_price_df) %>%
  addTiles() %>%
  addCircleMarkers(lat = ~MeanLat, lng = ~MeanLong,
                   color = ~pal(MeanPrice)) %>%
  addMarkers(data = top_places, lng = ~MeanLong, lat = ~MeanLat, popup = ~as.character(round(MeanPrice, digits=0))) %>%
  addLegend('bottomright', pal = pal, values = neighbourhoods_price_df$MeanPrice,
            title = 'Neighborhoods Prices',
            opacity = 0.5, # Adjusted opacity for less obstruction
            labFormat = labelFormat(prefix = " $"))
```

This map visualization presents the average Airbnb listing prices across different neighborhoods in New York City. Prices are indicated by the color intensity of the circle markers, with darker colors representing higher prices. The top ten neighborhoods with the highest average prices are marked with additional details in popups that display the exact average price when clicked. This interactive map allows users to visually compare pricing across the city and identify high-value areas at a glance.


### Figure 3

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Facet plot by neighbourhoods (with top 5 number of listings) showing scatterplots with linear regression lines of the total number of reviews and prices

top_5 <- df %>% group_by(neighbourhood) %>%
  summarise(Count=n())  %>%
  arrange(desc(Count)) %>%
  top_n(5, wt=Count)

df_selected_neighbourhoods <- df %>% 
  filter(neighbourhood %in% top_5$neighbourhood)

# Create the facet plot
p3 = ggplot(df_selected_neighbourhoods, aes(x = `number of reviews`, y = price)) +
  geom_point() +  
  geom_smooth(method = "lm", se = FALSE) +
  facet_wrap(~neighbourhood) + 
  labs(title = "Airbnb Listing Price vs Total Number of Reviews",
       x = "Total Number of Reviews",
       y = "Airbnb Listing Price") 

ggplotly(p3)
```

This facet plot explores the relationship between the number of reviews a listing has and its pricing across the five neighbourhoods with the highest count of listings in New York City. Each panel represents one neighbourhood and displays a scatterplot with a linear regression line, helping to visualize how consumer feedback (in the form of total reviews) might correlate with pricing strategies in different parts of the city. This analysis can reveal if more popular (frequently reviewed) listings tend to charge more or less, depending on the local market dynamics.

### Figure 4
```{r, message=FALSE, echo=FALSE}
# Listing Price by Minimum Nights
p4 <- ggplot(df, aes(x = as.factor(`minimum nights`), y = price)) +
  geom_boxplot() +
  labs(title = "Airbnb Listing Price by Minimum Nights Requirement",
       x = "Minimum Nights Requirement",
       y = "Price (per night)") +
  theme(legend.position = "bottom")
ggplotly(p4)
```

This boxplot displays the relationship between the minimum nights required for an Airbnb listing and its nightly price. Each box represents the price distribution for a specific minimum night requirement, showing the median price and the interquartile range. This visualization highlights how the length of stay required affects pricing, potentially offering insights into pricing strategies for short vs. long-term stays. It helps viewers understand pricing trends and anomalies associated with different stay durations in New York City Airbnb listings.

